A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-03-13 analysis/paper.Rmd
re-organize files and edit rmd file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '../') 
```
# Methods

@@

# Get data from simulation
load("./results/regdata_all.Rdata")
load("./results/inputs.RData")

@@

```{r, figure-plot, include=FALSE}
plot_fig <- function(fig_name, fig_country){
  # Load empirical data
  fv <- fread("./data/facevalidity.csv") %>% set_colnames(c("country","agegroup", "ceb","cs","tfr2010","tfr2000","hiv1990", "hiv2000", "hiv2010","art2005","art2006","art2007","art2008","art2009","art2010","art2011","art_prev2005","art_prev2006","art_prev2007","art_prev2008","art_prev2009","prop15to19_2010","prev15to19_2010","hiv2005","hiv2006","hiv2007","hiv2008","hiv2009")) %>% mutate(cd=ceb-cs)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Methods

@@

# Get data from simulation
load("results/regdata_all.Rdata")
load("results/inputs.RData")

@@

```{r, figure-plot, include=FALSE}
plot_fig <- function(fig_name, fig_country){
  # Load empirical data
  fv <- fread("data/facevalidity.csv") %>% set_colnames(c("country","agegroup", "ceb","cs","tfr2010","tfr2000","hiv1990", "hiv2000", "hiv2010","art2005","art2006","art2007","art2008","art2009","art2010","art2011","art_prev2005","art_prev2006","art_prev2007","art_prev2008","art_prev2009","prop15to19_2010","prev15to19_2010","hiv2005","hiv2006","hiv2007","hiv2008","hiv2009")) %>% mutate(cd=ceb-cs)
